Final paper detail checks and analyses

### 2021-03-08 Final_analyses_checks_notebook.Rmd
added sd for change scores to final checks

author: "Kirstin L Purves"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

@@

>>>>

author: "Kirstin L Purves"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

@@

### change scores

#### Retrospective
```{r means etc change overall retro}

vars <- dat.retro %>%
  select(gad.sum_score_base,gad.sum_score_retro,
         phq.sum_score_base,phq.sum_score_retro) %>%
  mutate(gad.retro.change = gad.sum_score_base - gad.sum_score_retro,
         phq.retro.change = phq.sum_score_base - phq.sum_score_retro) %>%
  select(gad.retro.change,
         phq.retro.change)

#### Prepandemic
```{r means etc change overall prepan}

vars <- dat.prepan %>%
  select(gad.sum_score_base,gad.sum_score_prepan,
         phq.sum_score_base,phq.sum_score_prepan,
         pcl.sum_score_base,pcl.sum_score_prepan) %>%
  mutate(gad.prepan.change = gad.sum_score_base - gad.sum_score_prepan,
         phq.prepan.change = phq.sum_score_base - phq.sum_score_prepan,
         pcl.prepan.change = pcl.sum_score_base - pcl.sum_score_prepan) %>%
  select(gad.prepan.change,
         phq.prepan.change,
         pcl.prepan.change)
